Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-16 snTomas.tex
minor text edits and updated light curve fitting fig

Next, we repeat the fitting, but without any warping of the templates
to account for differences in the continuum shape.  In this iteration
we only allow each template SED to be scaled in flux coherently at all
wavelengths.  As shown in Figure~\ref{fig:SpecFit}, we again find that
the \tomas\ SED can be matched by a normal Type Ia SN (SN 2011fe) at
redshift $z=1.31\pm0.02$.  \change{Fixing the redshift at the host redshift of
$z=1.3457$, we also find the best match is from SN 2011fe, with
$\chi^2/\nu=133.7/91$. }

@@

Setting aside the $z\sim1$ solution, all other template matches
provide a consistent redshift constraint of $z=1.31\pm0.01$,
regardless of whether the templates are warped to match the SN \tomas\
continuum shape.  The inferred age from these fits is $0\pm3$
rest-frame days from peak brightness, which is also consistent with
the observed light curve.

>>>>

Next, we repeat the fitting, but without any warping of the templates
to account for differences in the continuum shape.  In this iteration
we only allow each template SED to be scaled in flux coherently at all
wavelengths.  As shown in Figure~\ref{fig:SpecFit}, we again find that when the \change{redshift is allowed as a free parameter} 
the \tomas\ SED is best matched by a normal Type Ia SN (SN 2011fe) at
redshift $z=1.31\pm0.02$.  \change{Fixing the redshift to 
$z=1.3457$ of the host, we also find the best match is from SN 2011fe, with
$\chi^2/\nu=133.7/91$. }

@@

Setting aside the $z\sim1$ solution, all other template matches
provide a consistent redshift constraint of $z=1.31\pm0.02$,
regardless of whether the templates are warped to match the SN \tomas\
continuum shape.  The inferred age from these fits is $0\pm3$
rest-frame days from peak brightness, which is also consistent with
the observed light curve.
